Leadership across cultures and contexts: an exploratory analysis

### 2020-06-16 leadership_across_cultures_contexts.Rmd
Added mst-kNN analysis, perhaps to subsistute for the NMF analysis that we don't actually use.

Anthropology, on the other hand, has been criticized for exoticizing and essentializing diverse "Others" as part of its colonial history [@said1979; @abu2008]. @abu2008 [p. 470], for instance, notes that

>Anthropological discourse gives cultural difference (and the separation between groups of people it implies) the air of the self-evident. In this regard, the concept of culture operates much like its predecessor -- race -- even though in its twentieth-century form it has some important political advantages.

@@

df_compare2 %>% 
  filter(AIC_diff >= -2 & Estimate > 0.6) %>% 
  mutate(
    Type = map_chr(var, ~ str_split(., '_')[[1]][[1]]),
    Type = str_replace(Type, '\\.', ' '),
    Type = str_to_title(Type),
    `Percent of cultures` = 100*Estimate
  ) %>% 
  select(Type, Variable, `Percent of cultures`) %>% 
  arrange(-`Percent of cultures`) %>% 
  kable(digits = 1, caption = "Candidate universal dimensions of leadership. These dimensions were common in the ethnographic record (appearing in at least 60% of cultures), and did not appear to meaningfully vary by continental region, subsistence strategy,  group context, or leader sex.")

@@

coercive_plot <- coercive_plot + scale_x_log10()
anticoercive_plot <- anticoercive_plot + scale_x_log10() + scale_color_discrete()

p <-
  (coercive_plot + plot_elastic_coercive) / (anticoercive_plot + plot_elastic_anticoercive) +
  plot_annotation(
    title = 'Predictors of Coercive & No coercive authority',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
    )
ggsave('Figures/coercive_plot.pdf', p, width = 10, height = 8)
p
```

@@

@@

>>>>

Anthropology, on the other hand, has been criticized for exoticizing and essentializing diverse "Others" as part of its colonial history [@said1979; @abu2008]. In this regard, @abu2008 noted that the concept of culture operates much like its predecessor -- race.

@@

df_compare2 %>% 
  filter(AIC_diff >= -2 & Estimate > 0.6) %>% 
  mutate(
    Type = map_chr(var, ~ str_split(., '_')[[1]][[1]]),
    Type = str_replace(Type, '\\.', ' '),
    Type = str_to_title(Type),
    `Percent of cultures` = 100*Estimate
  ) %>% 
  select(Variable, Type, `Percent of cultures`) %>% 
  arrange(-`Percent of cultures`) %>% 
  kable(digits = 1, caption = "Candidate universal dimensions of leadership. These dimensions were common in the ethnographic record (appearing in at least 60% of cultures), and did not appear to meaningfully vary by continental region, subsistence strategy,  group context, or leader sex.")

@@

coercive_plot <- coercive_plot + ggtitle("Predictors of coercive authority") + scale_x_log10() + theme(plot.title = element_text(size = 12))

plot_elastic_coercive <- plot_elastic_coercive + ggtitle("Predictors of coercive authority") + theme(plot.title = element_text(size = 12))

anticoercive_plot <- anticoercive_plot + ggtitle("Predictors of no coercive authority") + scale_x_log10() + scale_color_discrete() + theme(plot.title = element_text(size = 12))

plot_elastic_anticoercive <- plot_elastic_anticoercive + ggtitle("Predictors of no coercive authority") + theme(plot.title = element_text(size = 12))

p <-
  (coercive_plot + plot_elastic_coercive) / (anticoercive_plot + plot_elastic_anticoercive) +
  plot_annotation(
    # title = 'Predictors of Coercive & No coercive authority',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
    )
ggsave('Figures/coercive_plot.pdf', p, width = 10, height = 8)
p
```

@@

### Logistic PCA

@@

### MST-kNN

```{r mstknn, fig.width=10, fig.height=10, fig.cap="Clusters of the combined leader function and quality variables formed by the mst-kNN algorithm. Dot size represents the number of text records with evidence for that variable. Dot color represents the type of variable."}
plot_mstknn
```
